Towards Reliable Machine Learning Deployments in the Cloud

### 2023-12-14 plots/combined/aft_comparison.tex

\begin{table}
\caption{Comparison of AFR Models on the COMBINED dataset.}
\label{tab:Combined}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -4732.34 & 0.82 & -4732.34 & 0.00 & 0.00 \\
cox & -- & 0.82 & -- & 0.00 & 0.00 \\
log_logistic & -4770.78 & 0.81 & -4770.78 & 0.00 & 0.00 \\
log_normal & -4788.03 & 0.81 & -4788.03 & 0.00 & 0.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models for the combined hardware and datasets.}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
Weibull & -6.36e+03 & 0.834 & -6.36e+03 & 0.00258 & 0.00195 \\
% Cox & -- & 0.847 & -- & 0.00224 & 0.00199 \\
Log-Logistic & -6.62e+03 & 0.862 & -6.62e+03 & 0.00274 & 0.00189 \\
Log-Normal & -6.6e+03 & 0.862 & -6.6e+03 & 0.0027 & 0.00186 \\
\bottomrule
\end{tabular}
\label{tab:Combined}
\end{table*}
